Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-31 tex/nusselt_paper.tex
hacked and slashed, part almost done

\begin{abstract}
Here we study stratified convection in the context of 
plane-parallel, polytropically stratified atmospheres. 
We hold the density stratification (\nrho) and Prandtl 
number (Pr) constant while varying the
Mach number (Ma) and the Rayleigh number (Ra) to determine 
the behavior of the Nusselt number (Nu), 
which quantifies the efficiency of convective heat transport.
As Ra increases and $\text{Ma} \rightarrow 1$, a scaling 
of Nu $\propto$ Ra$^{0.45}$ is observed.  
As Ra increases to a regime where Ma $\geq 1$,
this scaling gives way to a weaker Nu $\propto$ Ra$^{0.19}$. 
In the regime of Ma $\ll 1$, a consistent
Nu $\propto$ Ra$^{0.31}$ is retrieved,  reminiscent of the 
Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
\end{abstract}
\maketitle

%%%%% Body of the paper
\section{Introduction}
\refstepcounter{section}
\label{sec:intro}
Convection is essential to heat transport in the cores of high mass stars,
the envelopes of low mass stars, and the atmospheres of terrestrial and 
jovian planets.  The convective dynamics are influenced by the atmospheric 
stratification, which is small in some systems but extends up to 
14 density scale heights in the Sun's convective envelope.
Understanding the fundamental
properties of compressible convection in stratified media is essential
to characterizing systems in astrophysics and planetary sciences.  
Numerical constraints have often restricted studies of compressible
convection to moderately high Mach number (Ma), appropriate to regions near 
the Sun's surface.  Few fundamental properties of the 
low-Ma stratified convection which occurs in the deep solar interior are known.

Early numerical experiments on stratified convection
in two \cite{graham1975, chan&all1982,
hurlburt&all1984, cattaneo&all1990} and three 
\cite{cattaneo&all1991, brummell&all1996} dimensions
revealed a number of basic properties in the moderate-to-high 
Ma regime. In the widely-studied \RB (hereafter RB) problem, 
upflows and downflows are symmetrical and
the temperature gradient approaches zero in the convective interior 
causing the conductive flux to similarly 
disappear.  Highly stratified convection exhibits narrow downflow 
lanes and broad upflow regions.
Furthermore, the \emph{entropy} gradient is negated by convection 
rather than the temperature gradient, such
that in the presence of perfectly efficient convection a significant 
component of the flux is still carried by conduction.

In RB convection, there exist two primary control parameters: 
the Rayleigh number (Ra, the ratio of
buoyant driving to diffusive damping) and the Prandtl number 
(Pr, the ratio of viscous to thermal
diffusivity).  These numbers coupled with the aspect ratio of 
the physical domain and the boundary conditions
determine the dynamics of the convection.  In stratified atmospheres, 
in addition to specifying the equation of state and
fundamental properties of the gas, the two control parameters of 
RB convection are joined by the degree of
stratification across the domain and the characteristic 
Ma of the convective flows.  
Polytropically stratified atmospheres, such as those used in 
early studies, are an ideal extension of
RB convection into the stratified realm as the two additional 
control parameters are directly linked to
basic properties of the atmosphere.  The density stratification is 
set by the number of density scale heights
the atmosphere spans (\nrho), and Ma is controlled 
by the superadiabatic excess ($\epsilon$,
the deviation of the polytropic index from the adiabatic polytropic 
index \cite{graham1975}).

In this letter we study the behavior of convective heat transport, quantified by
the Nusselt number (Nu), in plane-parallel, two-dimensional, polytropically stratified atmospheres.  
$\epsilon$ and Ra are varied  while $\nrho$, Pr, and the aspect ratio are held
constant.  In section 
\ref{sec:experiment}, the construction of atmospheres, equations, and numerical methods are discussed.  
Results are described in section \ref{sec:results} and their implications are discussed
in section \ref{sec:discussion}.

\section{Experiment} 
\refstepcounter{section}
\label{sec:experiment}
In order to compare our results with previous studies and in an effort to examine a simplest case,
we study a fluid composed of monatomic ideal gas particles with an adiabatic index of $\gamma = 5/3$ and
whose equation of state is $P = R\rho T$. 
The initial atmosphere is a plane-parallel polytrope in which the gravitational acceleration
and conductive flux, $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0$, do not vary with depth. To
achieve the latter condition, both $\kappa$ and $\grad T_0$ are constant.
Under these assumptions, satisfying hydrostatic equilibrium produces a stratification of
\begin{equation}
\begin{split}
\rho_0(z) &= \rho_{t}(z_0 - z)^m, \\
T_0(z)    &= T_{t}(z_0 - z),
\label{eqn:polytrope}
\end{split}
\end{equation}
where $m = m_{ad} - \epsilon$ is the polytropic index.
The adiabatic polytropic index is $m_{ad} \equiv (\gamma-1)^{-1}$ and
the superadiabatic excess is $\epsilon$ which sets the scale 
of the entropy gradient, $\grad S_0 \propto -\epsilon$.
Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
By this choice, the non-dimensional length scale is the inverse temperature gradient scale and
the timescale is the isothermal sound crossing time of this unit length.
$z$ increases upwards within $[0, L_{z}]$, where $L_{z} = e^{n_{\rho}/m} - 1$ is
determined by $n_\rho$, the number of density scale heights the atmosphere spans.
The characteristic timescale of convective dynamics
is related to the atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
Throughout this letter, buoyancy time units are used and 
$n_{\rho} = 3$ such that the initial density varies by a factor of 20.
All atmospheres studied here have an aspect ratio of 4, such that $L_x = 4L_z$.

Atmospheric diffusivities are specified by the Rayleigh number and the Prandtl number.  The
non-dimensional Rayleigh number is
\begin{equation}
\text{Ra} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu\chi},
\end{equation}
where $\Delta S_0$ is the entropy difference between the top and bottom of the atmosphere, 
$c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat at constant pressure,
$\nu$ is the kinematic viscosity (viscous diffusivity), and $\chi$ is the thermal diffusivity.  
The relationship between the thermal and viscous diffusivities is
set by the Prandtl number, $\text{Pr} = \nu/\chi$.   We relate the dynamic viscosity, $\mu$, and the thermal conductivity,
$\kappa$, to their corresponding diffusivities such that 
$\nu \equiv \mu/\rho$ and $\chi \equiv \kappa/\rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
\rho^2$.  The atmospheres studied here with $n_{\rho} = 3$ experience an increase in the Rayleigh number 
by a factor of 400 across the domain.  This formulation leaves Pr
constant throughout the depth of the atmosphere. In this letter we impose $\text{Pr} = 1$ and
specify Ra at $z = L_z$.

At the constant values of $n_\rho$ and Pr used, the primary control parameters of convection are $\epsilon$
and Ra.  We decompose our atmosphere into the background polytrope ($\ln\rho_{0}, T_{0}$) and the fluctuations
about that background ($\bm{u}, \ln\rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
is reflected in the evolved values of these fluctuations, which follow the scaling of
$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$ for low values of $\epsilon$,
as in Fig. \ref{fig:ma_v_eps}.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{The maximum value of Ma which has been horizontally averaged and time averaged for $\geq 100 t_b$, 
beginning roughly $50t_b$ after
the start of simulations.  This time average is long enough that the profile is well converged
and error bars are negligible. (a) For $\epsilon \leq 0.1$,
a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
at $\text{Ra }= \{10^2, 10^5\}$ exists.
When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen.  
(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it
follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, consistent power laws are achieved throughout all
values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
\label{fig:ma_v_eps} }
\end{figure}

The Fully Compressible Navier-Stokes equations,
\begin{align}
&\begin{aligned}
&\frac{\partial \ln\rho}{\partial t} + \Div{\bm{u}} = -\bm{u}\cdot\grad\rho,
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial\bm{u}}{\partial t} + \grad T - &\nu\Div{\lilstressT} - \lilstressT\cdot\grad\nu = \\
&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + \nu\lilstressT\cdot\grad\ln\rho,
\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.\grad^2 T + \grad T\cdot\grad\chi\right) = \\
	&-\bm{u}\cdot\grad T - (\gamma-1)T\Div{\bm{u}} \\
	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
are evolved with a viscous stress tensor defined as
\begin{equation}
\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
	\label{eqn:stress_tensor}
\end{equation}

Taking an inner product of
Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
Eq. \ref{eqn:energy_eqn} reveals the full energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0.
	\label{eqn:energy_eqn_full}
\end{equation}
The convective flux is
$
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}.
$
Contributions from the enthalpy flux, $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
the kinetic energy flux, $\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
the potential energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
and the viscous flux, $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, must all be considered. 
%where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  
Understanding these flux terms and how they interact with the conductive flux, 
$\bm{F}_{\text{cond}} = -\kappa \grad T$, is crucial in characterizing
convective heat transport.

The atmosphere is contained between two impenetrable, stress free, fixed temperature boundaries at
the top and bottom of the domain such that $w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
is horizontally periodic. We utilize the novel Dedalus\footnote{http://dedalus-project.org/} pseudospectral framework 
 to time-evolve Eqs. 
\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit, third-order, four-step 
Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  Physical grid sizes range from
96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
By using IMEX timestepping, we implicitly step the stiff linear acoustic wave contribution and are able to
efficiently study flows at moderate ($\approx 1$) and very low ($\approx 10^{-4}$)
Ma (Fig. \ref{fig:ma_v_eps}b).  Our equations take the form
of the FC equations in \cite{lecoanet&all2014}, extended to include variable
$\nu$ and $\chi$, and we follow the approach there; this IMEX approach has been successfully 
tested against a nonlinear benchmark  of the compressible Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.

@@

We contend that this is the general form of the Nusselt number and illustrate this with a few limiting
cases. Convection eliminates
entropy stratification.  Under the Boussinesq approximation,
in which density variations are ignored, entropy stratification is directly proportional to temperature stratification
such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  The familiar Nu in the RB problem is
therefore retrieved from Eq. \ref{eqn:nusselt} because $\grad T_{\text{ad}} = 0$.  
In the case of polytropic convection,  $g \rightarrow 0$
as $\epsilon \rightarrow m_{ad} + 1$.
In this limit, $F_{\text{A}} \rightarrow 0$ and the
definition of the RB Nu is appropriate to use, as convection carries all of the
flux \cite{brandenburg&all2005}. 
However, as $\epsilon \rightarrow 0$, 
$\grad T_{\text{ad}}\rightarrow \grad T_0$ and increasingly
smaller velocity and thermodynamic perturbations are needed to achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
These perturbations carry what little flux exists in excess of the adiabatic, so the removal of 
$F_{\text{A}}$ in the numerator and denominator of Eq. \ref{eqn:nusselt} is essential for a reasonable Nu measurement.

\begin{figure}[b]
\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
\caption{Characteristic entropy fluctuations in evolved flows. The time- and horizontally-
averaged profile is removed in all cases.  At high
$\epsilon$ (a), shock systems form near the upper downflow lanes and propel shock-heated material deep within
the atmosphere at sufficiently high Ra.  At low $\epsilon$ but at the same Ra (b), shock systems are absent, 
but otherwise the dynamics are similar.  As Ra is increased (c), downflow lanes no longer span
the entirety of the domain and individual small blobs are responsible for carrying the flux.
\label{fig:entropy_snapshots} }
\end{figure}

Initial value problems were solved in which $T_1$ 
was filled with infinitesimal, random noise compared to $T_0$ and $\epsilon$.
Solutions were time-evolved until a long average of Nu showed little
variance with depth. By performing a linear stability analysis, we determined that the onset of convection
occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  
We studied Rayleigh
numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$.

At large Ma ($\epsilon = 0.5$), shock systems form in the upper atmosphere near downflow lanes 
(Fig. \ref{fig:entropy_snapshots}a) and propagate toward upflow lanes.  
Such systems were reported in
both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
These shocks heat material entering the downflows, affecting the dynamics and heat transport
of these systems.

Low Ma flows ($\epsilon = 10^{-4}$)
have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}b).
As Ra is increased to large values (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
no longer span the whole domain but rather break up into small packets which traverse the domain multiple
times before diffusing.  
While it has been suggested that pressure forces cause symmetry breaking in up- and downflows,
\cite{hurlburt&all1984}, this effect seems to be secondary to flows obeying mass conservation as they traverse
the stratified medium.  We observe low Ma cases where the double-roll systems such as those in
Fig. \ref{fig:entropy_snapshots}b contain one roll of increased pressure and one roll of decreased pressure
where the up- and downflows bound these regions of pressure disequilibrium.

>>>>

\begin{abstract}
Convection in astrophysical systems is stratified and
often occurs at high Rayleigh number (Ra) and low
Mach number (Ma).
Here we study stratified convection in the context of 
plane-parallel, polytropically stratified atmospheres. 
We hold the density stratification (\nrho) and Prandtl 
number (Pr) constant while varying
Ma and Ra to determine 
the behavior of the Nusselt number (Nu), 
which quantifies the efficiency of convective heat transport.
As Ra increases and $\text{Ma} \rightarrow 1$, a scaling 
of Nu $\propto$ Ra$^{0.45}$ is observed.  
As Ra increases to a regime where Ma $\geq 1$,
this scaling gives way to a weaker Nu $\propto$ Ra$^{0.19}$. 
In the regime of Ma $\ll 1$, a consistent
Nu $\propto$ Ra$^{0.31}$ is retrieved,  reminiscent of the 
Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
\end{abstract}
\maketitle

%%%%% Body of the paper
\section{Introduction}
\refstepcounter{section}
\label{sec:intro}
Convection is essential to heat transport in the cores of high mass stars,
the envelopes of low mass stars, and the atmospheres of terrestrial and 
jovian planets.  The convective dynamics in these astrophysical objects
are influenced by the atmospheric 
stratification, which is small in some systems (e.g. massive star cores)
but spans about
14 density scale heights in the Sun's convective envelope.
Understanding the fundamental
properties of compressible convection in stratified media is essential
to characterizing systems in astrophysics and planetary sciences.  
Numerical constraints have often restricted studies of compressible
convection to moderately high Mach number (Ma), appropriate to regions near 
the Sun's surface.  Few fundamental properties of the 
low-Ma stratified convection, which occurs in the deep solar interior, are known.

Early numerical experiments on stratified convection
in two \cite{graham1975, chan&all1982,
hurlburt&all1984, cattaneo&all1990} and three 
\cite{cattaneo&all1991, brummell&all1996} dimensions
revealed a number of basic properties in the moderate-to-high 
Ma regime. In the widely-studied \RB (hereafter RB) problem, 
upflows and downflows are symmetrical and
the temperature gradient approaches zero in the convective interior 
causing the conductive flux to similarly 
disappear.  These two hallmark characteristics of RB convection change
significantly when stratification is included.  Stratified convection 
exhibits narrow downflow lanes and broad upflow regions.
Furthermore, the \emph{entropy} gradient is negated by convection 
rather than the temperature gradient, such
that in the presence of perfectly efficient convection a significant 
component of the flux is still carried by conduction.

In RB convection, there exist two primary control parameters: 
the Rayleigh number (Ra, the ratio of
buoyant driving to diffusive damping) and the Prandtl number 
(Pr, the ratio of viscous to thermal
diffusivity).  These numbers coupled with the aspect ratio of 
the physical domain and the boundary conditions
determine the dynamics of the convection.  In stratified atmospheres, 
in addition to specifying the equation of state and
fundamental properties of the gas, the two control parameters of 
RB convection are joined by the degree of
stratification across the domain and the characteristic 
Ma of the convective flows.  
Polytropically stratified atmospheres, such as those used in 
early studies \cite{graham1975, chan&all1982, hurlburt&all1984, 
cattaneo&all1990, cattaneo&all1991, brummell&all1996} are an ideal extension of
RB convection into the stratified realm as the two additional 
control parameters are directly linked to
basic properties of the atmosphere.  The density stratification is 
set by the number of density scale heights (\nrho)
the atmosphere spans, and Ma is controlled 
by the superadiabatic excess ($\epsilon$),
the deviation of the polytropic index from the adiabatic polytropic 
index \cite{graham1975}.

In this letter we study the behavior of convective heat transport, 
quantified by the Nusselt number (Nu), in plane-parallel, 
two-dimensional, polytropically stratified atmospheres.  
We vary $\epsilon$ and Ra while holding $\nrho$, Pr, and the aspect ratio
constant.  We describe experimental methods in section 
\ref{sec:experiment}, including the construction of atmospheres, equations, and numerical methods.  
Results are described in section \ref{sec:results} and their implications are discussed
in section \ref{sec:discussion}.

\section{Experiment} 
\refstepcounter{section}
\label{sec:experiment}
We exmine the simplist stratified extension of RB by studying a
fluid composed of monatomic ideal gas particles with an adiabatic 
index of $\gamma = 5/3$ and whose equation of state is $P = R\rho T$. 
This is consistent with the approach used in earlier work.
The initial atmosphere is a plane-parallel polytrope in which 
the gravitational acceleration and conductive flux, 
$\bm{F}_{\text{cond,0}} = -\kappa \grad T_0$, do not vary with depth. To
achieve the latter condition, both $\kappa$ and $\grad T_0$ are constant.
Under these assumptions, satisfying hydrostatic 
equilibrium produces a stratification of
\begin{equation}
\begin{split}
\rho_0(z) &= \rho_{t}(z_0 - z)^m, \\
T_0(z)    &= T_{t}(z_0 - z),
\label{eqn:polytrope}
\end{split}
\end{equation}
where $m = m_{\text{ad}} - \epsilon$ is the polytropic index.
The adiabatic polytropic index is $m_{\text{ad}} \equiv (\gamma-1)^{-1}$ and
the superadiabatic excess is $\epsilon$ which sets the scale 
of the entropy gradient ($\grad S_0 \propto -\epsilon$).
A significant advance of this work is the ability to study large 
and small values of $\epsilon$, as will be discussed.
Thermodynamic variables are nondimensionalized at the 
top of the atmosphere as  $P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, 
requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
By this choice, the non-dimensional length scale is the inverse 
temperature gradient scale and the timescale is the isothermal 
sound crossing time of this unit length.
The height $z$ increases upwards within $[0, L_{z}]$, 
where $L_{z} = e^{n_{\rho}/m} - 1$ is
determined by $n_\rho$ and $\epsilon$.
The characteristic timescale of convective dynamics
is related to the atmospheric buoyancy time, 
$t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
Throughout this letter, we use buoyancy time units and 
choose $n_{\rho} = 3$ such that the 
initial density varies by a factor of 20.
All atmospheres studied here have an aspect ratio of 4, 
such that $L_x = 4L_z$.

Atmospheric diffusivities are specified by the Rayleigh number
and the Prandtl number.  The
non-dimensional Rayleigh number is
\begin{equation}
\text{Ra} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu\chi},
\end{equation}
where $\Delta S_0 = \epsilon\ln z_0$ is the entropy difference 
between the top and bottom of the atmosphere, 
$c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat 
at constant pressure, $\nu$ is the kinematic viscosity 
(the viscous diffusivity), and $\chi$ is the thermal diffusivity.  
The relationship between the thermal and viscous diffusivities is
set by the Prandtl number, $\text{Pr} = \nu/\chi$.   
The dynamic viscosity, $\mu$, and the thermal conductivity,
$\kappa$, relate to their corresponding diffusivities such that 
$\nu \equiv \mu/\rho$ and $\chi \equiv \kappa/\rho$.  We take
$\mu$ and $\kappa$ to be constant with height.
As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
\rho^2$.  The atmospheres studied here with $n_{\rho} = 3$ 
experience an increase in the Rayleigh number 
by a factor of 400 across the domain.  This formulation leaves Pr
constant throughout the depth of the atmosphere. 
In this letter we impose $\text{Pr} = 1$ and specify Ra at 
the top of the domain ($z = L_z$).

At the constant values of $n_\rho$ and Pr used, 
the primary control parameters of convection are $\epsilon$
and Ra.  We decompose our atmosphere into the background 
polytrope ($\ln\rho_{0}, T_{0}$) and the fluctuations
about that background ($\bm{u}, \ln\rho_{1}, T_{1}$),
which can be large.
The scaling of the entropy gradient with $\epsilon$
is reflected in the evolved values of these fluctuations, 
which follow the scaling of
$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$ 
for low values of $\epsilon$,
as in Fig. \ref{fig:ma_v_eps}.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{The maximum value of Ma which has been horizontally 
averaged and time averaged for $\geq 100 t_b$, 
beginning roughly $50t_b$ after
the start of simulations.  This time average is long 
enough that the profile is well converged
and error bars are negligible. (a) For $\epsilon \leq 0.1$,
a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
at $\text{Ra }= \{10^2, 10^5\}$ exists.
When $\epsilon \rightarrow m_{\text{ad}}$, 
large deviations from this power law are seen.  
(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ 
until it reaches the supersonic regime, at which point it
follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, 
consistent power laws are achieved throughout all
values of Ra studied, where 
$\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
\label{fig:ma_v_eps} }
\end{figure}

We evolve the Fully Compressible Navier-Stokes equations,
\begin{align}
&\begin{aligned}
&\frac{\partial \ln\rho}{\partial t} + \grad\cdot\bm{u} 
    = -\bm{u}\cdot\grad\rho,
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial\bm{u}}{\partial t} + \grad T - 
&\nu\grad\cdot\lilstressT - \lilstressT\cdot\grad\nu = \\
&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + 
\nu\lilstressT\cdot\grad\ln\rho,
\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.
    \grad^2 T + \grad T\cdot\grad\chi\right) = \\
	&-\bm{u}\cdot\grad T - (\gamma-1)T\grad\cdot{\bm{u}} \\
	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +
	\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
with the viscous stress tensor given by
\begin{equation}
\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + 
\frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right).
	\label{eqn:stress_tensor}
\end{equation}
Taking an inner product of
(\ref{eqn:momentum_eqn}) with $\bm{u}$ and adding it to 
(\ref{eqn:energy_eqn}) reveals the full energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0,
	\label{eqn:energy_eqn_full}
\end{equation}
where the convective flux is
$
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}
$
and the condcutve flux is $\bm{F}_{\text{cond}} = -\kappa \grad T$.
The individual contributions to $\bm{F}_{\text{conv}}$ are the enthalpy flux, 
$\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
the kinetic energy flux, 
$\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
the potential energy flux,
$\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
and the viscous flux, 
$\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, and all four
must all be considered. 
Understanding how these flux interact  
is crucial in characterizing convective heat transport.

The atmosphere is contained between two 
impenetrable, stress free, fixed temperature boundaries at
the top and bottom of the domain such that 
$w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
is horizontally periodic. We utilize the 
Dedalus\footnote{http://dedalus-project.org/} \cite{burns&all2016} pseudospectral framework 
 to time-evolve  
(\ref{eqn:continuity_eqn})-(\ref{eqn:energy_eqn}) 
using an implicit-explicit, third-order, four-step 
Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  
Physical grid sizes range from
96x384 grid points at the lowest values of 
Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
By using IMEX timestepping, we implicitly step the 
stiff linear acoustic wave contribution and are able to
efficiently study flows at moderate ($\approx 1$) and very low ($\approx 10^{-4}$)
Ma (Fig. \ref{fig:ma_v_eps}b).  Our equations take the form
of the FC equations in \cite{lecoanet&all2014}, extended to include variable
$\nu$ and $\chi$, and we follow the approach there; 
this IMEX approach has been successfully 
tested against a nonlinear benchmark  of the compressible 
Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.

@@

We contend that this is the general form of the Nusselt number
and illustrate this with a few limiting
cases. Convection eliminates
entropy stratification.  Under the Boussinesq approximation,
in which density variations are ignored, entropy stratification 
is directly proportional to temperature stratification
such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  
The familiar Nu in the RB problem is
therefore retrieved from (\ref{eqn:nusselt}) because $\grad T_{\text{ad}} = 0$.  
In the case of polytropic convection,  $g \rightarrow 0$
as $\epsilon \rightarrow m_{\text{ad}} + 1$.
In this limit, $\grad T_{\text{ad}} \rightarrow 0$ as well and the
definition of the RB Nu is appropriate to use, as convection carries all of the
flux \cite{brandenburg&all2005}. 
However, as $\epsilon \rightarrow 0$, 
$\grad T_{\text{ad}}\rightarrow \grad T_0$ and increasingly
smaller velocity and thermodynamic perturbations are needed to 
achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
These perturbations carry what little flux exists in 
excess of the adiabatic, so the removal of 
$F_{\text{A}}$ in the numerator and denominator of 
(\ref{eqn:nusselt}) is essential for a reasonable Nu measurement.

\begin{figure}[b]
\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
\caption{Characteristic entropy fluctuations in evolved flows. 
The time- and horizontally-averaged profile is removed in all cases.  (a) At high
$\epsilon$, shock systems form near the upper downflow lanes ($x \approx 45, z \approx 15-19$)
at sufficiently high Ra.
Shock-heated fluid then flows into the downflows as the shocks propagate across upflows.
(b) At low $\epsilon$ but at the same Ra, shock systems are absent, 
but otherwise the dynamics are similar.  (c) As Ra is increased, downflows no longer span
the entirety of the domain and individual small eddies are responsible for carrying the flux.
\label{fig:entropy_snapshots} }
\end{figure}

We evolve initial value problems in which $T_1$ is
filled with infinitesimal, random white noise compared to $T_0$ and $\epsilon$.
We filter the noise spectrum in coefficient space, such that 25\% of the coefficients
have power.
Solutions were time-evolved until a long average of Nu showed little
variance with depth. By performing a linear stability analysis, 
we determined that the onset of convection
occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$ respectively.  
We studied Rayleigh
numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$ and for $\epsilon = 10^{-4}$
and up to $10^3$Ra$_c$ for $\epsilon = 10^{-7}$.

At large Ma ($\epsilon = 0.5$), shock systems form in the upper atmosphere near downflow lanes 
(Fig. \ref{fig:entropy_snapshots}a) once Ra is sufficiently large.
These shocks propagate through upflow upflow regions.  
Such systems were reported in
both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
These shocks heat material entering the downflows, affecting the dynamics and heat transport
of these systems.

Low Ma flows ($\epsilon = 10^{-4}$)
have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}b)
to high Ma flows.
As Ra is increased to large values 
(Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
no longer span the whole domain but rather break up into 
small eddies which traverse the domain multiple
times before diffusing.  
While it has been suggested that pressure forces 
cause symmetry breaking in up- and downflows
\cite{hurlburt&all1984}, at low $\epsilon$ this 
effect seems to be secondary to flows obeying mass conservation as they traverse
the stratified medium.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
\caption{Time-averaged vertical flux profiles ($F_{\text{z}}$)
for (a) high and (b) low Ma flows at $\text{Ra }= 10^6$.  
All fluxes are defined as in (\ref{eqn:energy_eqn_full}) and 
normalized by $F_{\text{ref}} - F_{\text{A}}$, as in (\ref{eqn:nusselt}).
The dashed lines correspond to the
enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  
The grey dash-dot line is the
viscous flux and the green dotted line is the conductive flux with the 
adiabatic contribution removed. Viscous and
potential energy fluxes are negligible in (a) and are not shown.    
The solid black line is
Nu, the properly normalized sum of all the fluxes \label{fig:flux_profiles} }
\end{figure}
